High Performance Computing Project\\ Parallelization of the Probabilistic Roadmap Method with GPU Acceleration

### 2016-06-01 paper/presentation.tex
presentation

\begin{frame}
	\frametitle{Gliederung}
	\tableofcontents
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%
\section{Motivation}
\begin{frame}
\frametitle{Motivation}
	\begin{center}
		\includegraphics[height=4cm]{configspacetrafo.png}
	\end{center}
	\begin{itemize}
		\item Problem: find a feasible trajectory of a robot through a setting of obstacles
		\item often necessary to pass feasible initial tajectories to optimization algorithms
	\end{itemize}
\end{frame}

@@

%%%%%%%%%%%%%%%%%%%%%%%
\section{Robotics Application}
\begin{frame}
\frametitle{Robotics Application}
	\begin{center}
		\includegraphics[height=3cm]{configspacetrafo.png}
	\end{center}
	\begin{itemize}
		\item For each linear connection, every intermediate configuration has to be checked for collisions
		\item $\Rightarrow$ Many independent and similar kinematics and collision calculations
		\item $\Rightarrow$ Well suited for usage of GPU
	\end{itemize}
\end{frame}

@@

>>>>

%\begin{frame}
%	\frametitle{Gliederung}
%	\tableofcontents
%\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%
%\section{Motivation}
\begin{frame}
\frametitle{Motivation}
	\begin{center}
		\includegraphics[height=4cm]{configspacetrafo.png}
	\end{center}
	\begin{itemize}
		\item Problem: find a feasible trajectory of a robot through a setting of obstacles
		\item often necessary to pass feasible initial tajectories to optimization algorithms
	\end{itemize}
\end{frame}

@@

%%%%%%%%%%%%%%%%%%%%%%%
%\section{Robotics Application}

\begin{frame}
\frametitle{Robotics Application}
	\begin{center}
		\includegraphics[height=3cm]{configspacetrafo.png}
	\end{center}
	\begin{itemize}
		\item For each linear connection, every intermediate configuration has to be checked for collisions
		\item $\Rightarrow$ Many independent and similar kinematics and collision calculations
		\item $\Rightarrow$ Well suited for usage of GPU
		\item Every GPU thread can make one intermediate test
	\end{itemize}
\end{frame}

%\section{Parallelization}

@@

\begin{frame}
\frametitle{Second Level of Parallelization}
Version 3: Asynchronous, overlapping kernel calls

\begin{center}
\resizebox{!}{0.8\textheight}{%
\begin{tikzpicture}
	\tikzset{mywidth/.style={minimum width=2.5cm},};
	\node[block, mywidth] (l1) {\textbf{Worker 1}};
	\node[frameless, mywidth, below=of l1, minimum height=1.5cm] (l2) {$\vdots$};
	\node[block, mywidth, below=of l2] (l3) 	{\begin{tabular}{c}
										generate\\ nodes, \\
										start kernel
									\end{tabular}};
	\node[frameless, mywidth, below=of l3, minimum height=2cm] (l6) {};
	\node[frameless, mywidth, below=of l6] (l7) {};
	\node[block, mywidth, below=of l7] (l11)	{\begin{tabular}{c}
										receive\\ result, \\
										store nodes \\ 
										and edges
									\end{tabular}};
	\node[frameless, mywidth, below=of l11] (l12) {$\vdots$};

	\node[block, mywidth, right=of l1] (r1) {\textbf{Worker 2}};
	\node[frameless, mywidth, right=of l2, minimum height=1.5cm] (r2) {$\vdots$};
	\node[frameless, mywidth, right=of l3] (r3) {};
	\node[block, mywidth, right=of l6] (r6)	{\begin{tabular}{c}
										receive\\ result, \\
										store nodes \\
										and edges
									\end{tabular}};
	\node[block, mywidth, right=of l7] (r7) 	{\begin{tabular}{c}
										generate\\ nodes, \\
										start kernel
									\end{tabular}};
	\node[frameless, mywidth, right=of l12] (r12) {$\vdots$};

	\node[frameless, left=of l1] (g1) {};
	\node[block, below=of g1, minimum height=14cm] (graph) {\rotatebox{90}{\textbf{Graph}}};

	%gpu column
	\tikzset{gpuwidth/.style={minimum width=0.8cm},};

	\node[block, right=2cm of r1, minimum width=2.5cm] {\textbf{GPU}};
	\node[frameless, right=2cm of r2, gpuwidth] (topa) {$\vdots$};
	\node[frameless, right=of topa, gpuwidth] (topb) {$\vdots$};
	\node[block2, below=0.7cm of topa, gpuwidth, minimum height=4.3cm] (stream1a) {\rotatebox{90}{kernel}};
	\node[block2, below=2.3cm of stream1a, gpuwidth, minimum height=4.2cm] (stream1b) {\rotatebox{90}{kernel}};
	\node[frameless, below=0.3cm of stream1b, gpuwidth] (bota) {$\vdots$};

	\node[block2, below=2.2cm of topb, gpuwidth, minimum height=7.6cm] (stream2) {\rotatebox{90}{kernel}};
	\node[frameless, right=of bota, gpuwidth] (botb) {$\vdots$};

	%EDGES

	\path[-latex',thick]	(graph.east |- l3.west) edge (l3.west)
					(l11.west) edge (graph.east |- l11.west);
	\path[-latex',thick]	(graph.east |- r7.west) edge (r7.west)
					(r6.west) edge (graph.east |- r6.west);
	\path[dotted,thick]	(l2) edge (l3)
					(l3) edge (l11)
					(l11) edge (l12)
					(r2) edge (r6)
					(r6) edge (r7)
					(r7) edge (r12);

	\path[-latex',thick]	(r6.east -| stream1b.west) edge (r6.east);
	\path[-latex',thick]	(r7.east) edge (r7.east -| stream1b.west);

	\path[-,thick]		(l3.east) edge (l3.east -| stream1a.west);
	\path[-latex',thick]	(stream1a.east |- l3.east) edge (l3.east -| stream2.west);
	\path[latex'-,thick]		(l11.east) edge (l11.east -| stream1b.west);
	\path[-,thick]		(stream1b.east |- l11.east) edge (l11.east -| stream2.west);
